---
title: "DOH_ztest"
author: "Nhung"
date: '2022-09-23'
output: html_document
---

```{r}
library(tidyverse)
```


```{r}
m <- read_csv("DOH.csv")
m

```


```{r}
table(m$RiskFactor_2_CTA)
table(m$SocialDisparities_3_CTA)
table(m$Debunk_4_CTA)
table(m$UncertaintyReduction_5_CTA)
table(m$Testing_6_CTA)
table(m$Vaccine_7_CTA)

```


```{r}
p <- read_csv("DOH1.csv")
p
```

```{r}
colnames(p)
```

```{r}
summary(p)
```


```{r}
p1 <- p %>% 
  mutate(RiskFactor_2_CTA = recode(RiskFactor_2_CTA, '88' = 0, 
                                                       '0'=1, '1'=1, '2'=1, '3'=1, '4'=1, '5'=1,
                                                        '6'=1, '7'=1, '8'=1, '9'=1, '10'=1, 
                                                        '11'=1, '12'=1, '13'=1, '14'= 1, '15' =1, 
                                                        '16' =1, '18' =1, '20'=1, '25'=1, '26'=1)) %>%  
         
   mutate(SocialDisparities_3_CTA = recode(SocialDisparities_3_CTA, '88' = 0, 
                                                        '0'=1, '1'=1, '2'=1, '3'=1, '4'=1, '5'=1,
                                                        '6'=1, '7'=1, '8'=1, '9'=1, '10'=1, 
                                                        '11'=1, '12'=1, '13'=1, '14'= 1, '15' =1, 
                                                        '26'=1)) %>% 
   
   mutate(Debunk_4_CTA = recode(Debunk_4_CTA,'88' = 0, 
                                                '0'=1, '1'= 1, '2'=1, '3'=1, '4'=1, '5'=1,
                                                        '6'=1, '7'=1, '8'= 1, '9'= 1, '10'=1, 
                                                        '11'=1, '15' =1)) %>% 
          
  
   mutate(UncertaintyReduction_5_CTA =recode(UncertaintyReduction_5_CTA, '88' = 0, 
                                                        '0'=1, '1'=1, '2'=1,  '3'=1, '4'=1, '5'=1,
                                                        '6'=1, '7'=1, '8'= 1, '9'=1, '10'=1, 
                                                        '11'=1, '12'=1, '13'=1, '14'= 1, '15' =1, 
                                                        '16' =1, '17'= 1, '18' =1, '25'=1, '26'=1)) %>% 
  
     mutate(Testing_6_CTA = recode(Testing_6_CTA, '88' = 0, 
                                                   '0'=1, '1'=1, '2'=1, '3'=1, '4'=1, '5'=1,
                                                    '6'=1, '7'=1, '8'=1, '9'=1, '10'=1, 
                                                    '11'=1, '12'=1, '13'=1, '14'= 1, '15' =1, 
                                                    '18' =1, '25'=1, '26'=1)) %>%  
         
      mutate( Vaccine_7_CTA = recode(Vaccine_7_CTA, '88' = 0, 
                                                  '0'=1, '1'=1, '2'=1, '3'=1, '4'=1, '5'=1,
                                                  '6'=1, '7'=1, '8'=1, '9'=1, '15' =1)) %>% 
  mutate( Action_13_CTA = recode(Action_13_CTA, '88' = 0, 
                                                  '0'=1, '1'=1, '2'=1, '3'=1, '4'=1, '5'=1,
                                                  '6'=1, '7'=1, '8'=1, '9'=1, '15' =1,  '16' =1, '18' =1, 
                                                  '25'=1, '26'=1))

p1 
         
```




```{r}
table(p1$Action_13_CTA)
table(p1$Positive_14a_Number)
table(p1$Negative_14b_Number)
table(p1$Individual_14c_Number)
table(p1$Collective_14d_Number)

```



```{r}
p2 <- p1 %>% 
  select(-"Mental_8_YesNo", 
         -"Emotion_9_Number", 
         - "Praise_10_Number", 
         -"Pop_11_Number", 
         -"Language_12_Number") %>% 
  mutate(efficacy_total = Individual_14c_Number + Collective_14d_Number) %>% 
  mutate(efficacy_total1 = Negative_14b_Number + Positive_14a_Number) %>%
  mutate(Gov_poli = factor(Gov_poli, levels = c(1,2), labels = c("Republican", "Democratic"))) %>% 
  mutate(Trifecta = factor(Trifecta, levels = c(1,2,3), labels = c("Republican", "Democratic", "Mixture")))
p2
levels(p2$Gov_poli)
```

```{r}
ggplot(p2, aes(Action_13_CTA , fill = RiskFactor_2_CTA)) +
  geom_histogram() +
  scale_x_log10() +
  facet_grid(RiskFactor_2_CTA ~ ., margins=TRUE, scales="free_y")
```


```{r}
ggplot(p2, aes(Positive_14a_Number , fill = SocialDisparities_3_CTA)) +
  geom_histogram() +
  scale_x_log10() +
  facet_grid(SocialDisparities_3_CTA ~ ., margins=TRUE, scales="free_y")
```


```{r}
ggplot(p2, aes(Negative_14b_Number, fill = RiskFactor_2_CTA)) +
  geom_histogram() +
  scale_x_log10() +
  facet_grid(RiskFactor_2_CTA ~ ., margins=TRUE, scales="free_y")
```

```{r}
ggplot(p2, aes(Individual_14c_Number, fill = RiskFactor_2_CTA)) +
  geom_histogram() +
  scale_x_log10() +
  facet_grid(RiskFactor_2_CTA ~ ., margins=TRUE, scales="free_y")
```

```{r}
library("dplyr")
library("ggpubr")
ggdensity(p2$Action_13_CTA, 
          main = "Density plot of Action_13_CTA",
          xlab = "Individual_Action_13_CTA")
```

```{r}
library("dplyr")
library("ggpubr")
ggdensity(p2$Positive_14a_Number, 
          main = "Density plot of Positive_14a_Number",
          xlab = "Individual_Positive_14a_Number")
```

```{r}
library("dplyr")
library("ggpubr")
ggdensity(p2$Negative_14b_Number, 
          main = "Negative_14b_Number",
          xlab = "Negative_14b_Number")
```



```{r}
library("dplyr")
library("ggpubr")
ggdensity(p2$Individual_14c_Number, 
          main = "Density plot of Individual_14c_Number",
          xlab = "Individual_14c_Number")
```



```{r}
library("dplyr")
library("ggpubr")
ggdensity(p2$Collective_14d_Number, 
          main = "Density plot of collective efficacy",
          xlab = "Collective efficacy")
```


```{r}
library("dplyr")
library("ggpubr")
ggdensity(p2$minority_percent, 
          main = "Density plot of minority_percent",
          xlab = "minority_percent")
```

minority_percent Poverty_percent
```{r}
library("dplyr")
library("ggpubr")
ggdensity(p2$Poverty_percent, 
          main = "Density plot of Poverty_percent",
          xlab = "Poverty_percent")
```


```{r}
summary(p1)
```


# z-test efficacy positive - negative

#https://rpubs.com/nguyenminhsang/two-sample_z-test

```{r}
# Set difference to be tested
d0<-0
d0

# Set standard deviation of sample with status 0
sigma0<-sd(p1$Positive_14a_Number)
sigma0

# Set standard deviation of sample with status 1
sigma1<-sd(p1$Negative_14b_Number)
sigma1


#Calculate the two means 
 mean_positive <- mean(p1$Positive_14a_Number)
 mean_positive
 mean_negative <- mean(p1$Negative_14b_Number)
 mean_negative
 
 #Calculate the two lengths
n_positive<-length(p1$Positive_14a_Number)
n_positive
n_negative<-length(p1$Negative_14b_Number)
n_negative

# Calculate test statistic and two-sided p-value

z<-((mean_positive- mean_negative)-d0)/
  sqrt(sigma0^2/n_positive+
         sigma1^2/n_negative)
z

p_value=2*pnorm(-abs(z))
p_value

```

###RQ1: To what extent do state health departments use self-efficacy statements (Q14 a vs Q14b AND Q14c vs. Q14d) in their Facebook posts between Jan-Dec, 2020?

# z-test efficacy positive - negative 

```{r}
# Set difference to be tested
d1_0<-0
d1_0

# Set standard deviation of sample with status 0
sigma1_0<-sd(p1$Individual_14c_Number)
sigma1_0

# Set standard deviation of sample with status 1
sigma1_1<-sd(p1$Collective_14d_Number)
sigma1_1


#Calculate the two means 
 mean_individual <- mean(p1$Individual_14c_Number)
 mean_individual 
 mean_collective <- mean(p1$Collective_14d_Number)
 mean_collective
 
 #Calculate the two lengths
n_individual <-length(p1$Individual_14c_Number)
n_individual 
n_collective<-length(p1$Collective_14d_Number)
n_collective

# Calculate test statistic and two-sided p-value

z1 <-((mean_individual-mean_collective)-d1_0)/
  sqrt(sigma1_0^2/n_individual + 
         sigma1_1^2/n_collective)
z1

p_value1 =2*pnorm(-abs(z))
p_value1 

```


###RQ3:  How do self-efficacy statements in posts differ between states governed by Democrat and Republican governors?

```{r}
#fit0 <- t.test(
#  formula = efficacy_total1 ~ Gov_poli, 
#  data = p2, 
#  paired = FALSE, 
 # var.equal = TRUE)
#(fit0)
#library(parameters)
#model_parameters(fit0)
```



```{r}
fit <- t.test(
  formula = efficacy_total ~ Gov_poli, 
  data = p2, 
  paired = FALSE, 
  var.equal = FALSE
)
(fit)
library(parameters)
model_parameters(fit)
```

```{r}
fit1 <- t.test(
  formula = Positive_14a_Number ~ Gov_poli, 
  data = p2, 
  paired = FALSE, 
  var.equal = FALSE
)
(fit1)
library(parameters)
model_parameters(fit1)
```



```{r}
fit2 <- t.test(
  formula = Negative_14b_Number ~ Gov_poli, 
  data = p2, 
  paired = FALSE, 
  var.equal = FALSE
)
(fit2)
library(parameters)
model_parameters(fit2)
```




```{r}
fit3 <- t.test(
  formula = Individual_14c_Number ~ Gov_poli, 
  data = p2, 
  paired = FALSE, 
  var.equal = FALSE
)
(fit3)
library(parameters)
model_parameters(fit3)
```


```{r}
fit4 <- t.test(
  formula = Collective_14d_Number ~ Gov_poli, 
  data = p2, 
  paired = FALSE, 
  var.equal = FALSE
)
(fit1)
library(parameters)
model_parameters(fit4)
```



```{r}
library(effectsize)
cohens_d(fit)
cohens_d(fit1)
cohens_d(fit2)
cohens_d(fit3)
cohens_d(fit4)

```


###RQ4:  How do self-efficacy statements in posts differ between states governed by Democrat and Republican states?

```{r}
colnames(p2)
```

```{r}
levels(p2$Trifecta)
```


```{r}
fit_0 <- aov(formula = efficacy_total ~ Trifecta, data = p2)
summary(fit_0)
model_parameters(fit_0)
```


```{r}
library(ggeffects)
gge_0 <- ggeffect(fit_0, "Trifecta")
gge_0
plot(gge_0, connect.lines = TRUE)
```



```{r}
fit_1 <- aov(formula = Positive_14a_Number ~ Trifecta, data = p2)
summary(fit_1)
model_parameters(fit_1)
```

```{r}
gge_1 <- ggeffect(fit_1, "Trifecta")
gge_1
plot(gge_1, connect.lines = TRUE)
```


```{r}
fit_2 <- aov(formula = Negative_14b_Number ~ Trifecta, data = p2)
summary(fit_2)
model_parameters(fit_2)
```

```{r}
gge_2 <- ggeffect(fit_2, "Trifecta")
gge_2
plot(gge_2, connect.lines = TRUE)
```

```{r}
fit_3 <- aov(formula = Individual_14c_Number ~ Trifecta, data = p2)
summary(fit_3)
model_parameters(fit_3)

```

```{r}
gge_3 <- ggeffect(fit_3, "Trifecta")
gge_3
plot(gge_3, connect.lines = TRUE)
```

```{r}
fit_4 <- aov(formula = Collective_14d_Number ~ Trifecta, data = p2)
summary(fit_4)
model_parameters(fit_4)
```


```{r}
gge_4 <- ggeffect(fit_4, "Trifecta")
gge_4
plot(gge_4, connect.lines = TRUE)
```

RQ5: How does the socio-economic status affect use of individual/collective self-efficacy in health communication messages? 

```{r}
p2 
```
```{r}
colnames(p2)
```


```{r}
p3 <-p2 %>% 
  rename( White_percent = "White_\bpercent") %>% 

  select(minority_percent, Poverty_percent, Positive_14a_Number, Negative_14b_Number, Individual_14c_Number, Collective_14d_Number, efficacy_total)
p3
```



```{r}
library(correlation)
correlation(p3)
```

```{r}
rmat <- correlation(p3)
plot(summary(rmat))
```

###RQ6: To what extent do state health departments use call to action in relations to risk (Q2, 3,4,5,6,7)? 

```{r}
p2
```

```{r}
colnames(p2)
```

```{r}
p2$RiskFactor_2_CTA
```


```{r}
fita_0 <- t.test(
  formula = Action_13_CTA ~ RiskFactor_2_CTA, 
  data = p2, 
  paired = FALSE, 
  var.equal = FALSE
)
fita_0

library(parameters)
model_parameters(fita_0)
```


```{r}
fita_1 <- t.test(
  formula = Action_13_CTA ~ SocialDisparities_3_CTA, 
  data = p2, 
  paired = FALSE, 
  var.equal = FALSE
)
fita_1
model_parameters(fita_1)
```




```{r}
fita_2 <- t.test(
  formula = Action_13_CTA ~ Debunk_4_CTA, 
  data = p2, 
  paired = FALSE, 
  var.equal = FALSE
)
fita_2
model_parameters(fita_2)
```


```{r}
fita_3 <- t.test(
  formula = Action_13_CTA ~ UncertaintyReduction_5_CTA, 
  data = p2, 
  paired = FALSE, 
  var.equal = FALSE
)
fita_3
model_parameters(fita_3)
```


```{r}
fita_5 <- t.test(
  formula = Action_13_CTA ~ Testing_6_CTA, 
  data = p2, 
  paired = FALSE, 
  var.equal = FALSE
)
fita_5
model_parameters(fita_5)
```


```{r}

fita_6 <- t.test(
  formula = Action_13_CTA ~ Vaccine_7_CTA, 
  data = p2, 
  paired = FALSE, 
  var.equal = FALSE
)
fita_6
model_parameters(fita_6)
```


```{r}
library(effectsize)
cohens_d(fita_0)
cohens_d(fita_1)
cohens_d(fita_2)
cohens_d(fita_3)
cohens_d(fita_5)
cohens_d(fita_6)
```



RQ7: How does the socio-economic status affect use of call to action in health communication messages? 

```{r}
p4 <- p2 %>% 
  select(minority_percent, Poverty_percent, Action_13_CTA)
p4
```

```{r}
correlation(p4)
rmat1 <- correlation(p4)
plot(summary(rmat1))
```
```{r}
fit_0a <- lm(Action_13_CTA  ~ minority_percent,  data = p4 )
fit_0a
summary(fit_0a)
model_parameters(fit_0a)
library(ggeffects)
plot(ggpredict(fit_0a, terms = "minority_percent"))
```

```{r}
fit_0b <- lm(Action_13_CTA  ~ Poverty_percent,  data = p4 )
fit_0b
summary(fit_0b)
model_parameters(fit_0b)
library(ggeffects)
plot(ggpredict(fit_0b, terms = "Poverty_percent"))
```

```{r}
library(performance)
compare_performance(fit_0a, fit_0b, metrics = c("R2", "R2_adj"))
```


Partial effects 

```{r}
fit_1a <- lm (Action_13_CTA  ~ minority_percent + Poverty_percent, data = p4 )
fit_1a
summary(fit_1a)
```

```{r}
parameters(fit_1a)
performance(fit_1a)
plot(ggpredict(fit_1a, terms = c("minority_percent", "Poverty_percent[10,12,15]")))
```


Simple effect

```{r}
fit_1b <- lm (Action_13_CTA  ~ minority_percent * Poverty_percent, data = p4 )
fit_1b
summary(fit_1b)
```


```{r}
parameters(fit_1b)
performance(fit_1b)
plot(ggpredict(fit_1b, terms = c("minority_percent", "Poverty_percent[10,12,15]")))
```

# no need centering because 0 % is meaningful 



RQ8: How does efficacy statements predict call to actions? 


```{r}
p5 <- p2 %>% 
  select(Action_13_CTA, Positive_14a_Number, Negative_14b_Number, Individual_14c_Number, Collective_14d_Number)
p5
```
```{r}
correlation(p5)
rmat_1 <- correlation(p5)
plot(summary(rmat_1))

```

Total effects 

```{r}
fita_0 <- lm(Action_13_CTA ~ Positive_14a_Number , data = p5 )
fita_0
summary (fita_0)
fita_1 <- lm(Action_13_CTA ~ Negative_14b_Number, data = p5 )
fita_1
summary (fita_1)


```


```{r}
fita_2<- lm(Action_13_CTA ~ Individual_14c_Number, data = p5 )
fita_2
summary (fita_2)
fita_3 <- lm(Action_13_CTA ~ Collective_14d_Number, data = p5 )
fita_3
summary (fita_3)
```


```{r}
library(performance)
compare_performance(fita_0, fita_1, fita_2, fita_3, metrics = c("R2", "R2_adj"))
```




Partial effects

```{r}
fit1_0 <- lm(Action_13_CTA ~ Positive_14a_Number + Negative_14b_Number, data = p5 )
fit1_0
parameters(fit1_0)
performance(fit1_0)
plot(ggpredict(fit1_0, terms = c("Positive_14a_Number", "Negative_14b_Number[1,3,6]")))
```



```{r}
fit1_1 <- lm(Action_13_CTA ~ Individual_14c_Number + Collective_14d_Number, data = p5 )
fit1_1
parameters(fit1_1)
performance(fit1_1)
plot(ggpredict(fit1_1, terms = c("Individual_14c_Number", "Collective_14d_Number[2,4,8]")))
```


Simple effects

```{r}
fit1_1 <- lm(Action_13_CTA ~ Positive_14a_Number * Negative_14b_Number, data = p5 )
fit1_1
parameters(fit1_1)
performance(fit1_1)
plot(ggpredict(fit1_1, terms = c("Positive_14a_Number", "Negative_14b_Number[1,3,6]")))
```


```{r}
fit_check1_1 <- check_model(fit1_1)
fit_check1_1
```



```{r}
fit1_2 <- lm(Action_13_CTA ~ Individual_14c_Number * Collective_14d_Number, data = p5 )
fit1_2
parameters(fit1_2)
performance(fit1_2)
plot(ggpredict(fit1_2, terms = c("Individual_14c_Number", "Collective_14d_Number[2,4,8]")))
```


```{r}
fit_check1_2 <- check_model(fit1_2)
fit_check1_2
```




#https://stats.oarc.ucla.edu/r/dae/zinb/

```{r}
require(ggplot2)
require(pscl)
require(MASS)
require(boot)
```
```{r}
library(ggplot2)
library(pscl)
library(MASS)
library(boot)
```

```{r}
require(nonnest2)
require(lmtest)
```


```{r}
p2
```


```{r}
colnames(p2)
```


###Zero inflated models 

#Positive_14a_Number vs. RiskFactor_2_CTA (contibous vs. categories)

```{r}
m1_01 <- zeroinfl(Positive_14a_Number ~ RiskFactor_2_CTA, 
  data = p2, dist = "negbin")
summary(m1_01)
```

#Positive_14a_Number ~ minority_percent (continous vs. contious)
```{r}
m1_0 <- zeroinfl(Positive_14a_Number ~ minority_percent, 
  data = p2, dist = "negbin")
summary(m1_0)
```


```{r}
m1_1 <- zeroinfl(Negative_14b_Number ~ minority_percent, 
  data = p2, dist = "negbin")
summary(m1_1)
```

```{r}
m1_2 <- zeroinfl(Individual_14c_Number ~ minority_percent, 
  data = p2, dist = "negbin")
summary(m1_2)
```

```{r}
m1_2 <- zeroinfl(Collective_14d_Number ~ minority_percent, 
  data = p2, dist = "negbin")
summary(m1_2)
```


###Risk factor vs. efficacy 

#??? Is this the interactions? How to interprete that. 

```{r}
m1 <- zeroinfl(Action_13_CTA ~ efficacy_total|RiskFactor_2_CTA,
  data = p2, dist = "negbin")
summary(m1)
```


```{r}
m2 <- zeroinfl(Action_13_CTA ~ efficacy_total1|RiskFactor_2_CTA,
  data = p2, dist = "negbin")
summary(m2)
```






########################################################################
```{r}
#DOH_uncetainty <- p %>% 
 #  filter(UncertaintyReduction_5_CTA != 88)
# DOH_uncetainty
```


```{r}
#DOH_no88 <- p[p[,"RiskFactor_2_CTA"] != 88 | 
 #               p[,"SocialDisparities_3_CTA"] != 88 | 
 #               p[,"Debunk_4_CTA"] != 88 |  
  #                p[,"UncertaintyReduction_5_CTA"] != 88 | 
  #                p[,"Testing_6_CTA"] !=88 | 
  #                p[,"Vaccine_7_CTA"]!= 88,
   #             ]
 # 
 #  # DOH_no88
```


```{r}
 # RiskFactor_2_CTA 
 # SocialDisparities_3_CTA 
 # Debunk_4_CTA 
 # UncertaintyReduction_5_CTA 
 # Testing_6_CTA 
 # Vaccine_7_CTA 
 # a
```





```{r}
#a <- p[p$RiskFactor_2_CTA > 0 & p$SocialDisparities_3_CT > 0, 
 # p$Debunk_4_CTA > 0 & p$UncertaintyReduction_5_CTA > 0, 
 #   p$Testing_6_CTA > 0 & p$Vaccine_7_CTA > 0, 
 # ]
#a 
```


```{r}
library("dplyr")  
 # a <- filter(p, RiskFactor_2_CTA != 88)
 # b <- filter(p, SocialDisparities_3_CTA != 88)
 # c <- filter(p, Debunk_4_CTA != 88)
 # d <- filter(p, UncertaintyReduction_5_CTA != 88)
 # e <- filter(p, Testing_6_CTA != 88)
 # f <- filter(p, Vaccine_7_CTA  != 88)
 # k <- filter(p, Action_13_CTA  != 88)
 # a
 # b
 # c
 # d
 # e
 # f

```

```{r}
 # DOH_no88 <- rbind(a, b, c, d, e,f)
 # DOH_no88
```

